---
title: "GEDSpy - scRNAseq data global alterations enrichment"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly       
    highlight: tango
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    self_contained: true
    css: "custom.css"
---


```{r setup, include=FALSE}
install_if_missing <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
  }
}

packages <- c("knitr", "dplyr", "kableExtra")
lapply(packages, install_if_missing)

library(knitr)
library(dplyr)
library(kableExtra)

set.seed(123)



show_image <- function(path, caption = NULL, width = NULL, height = NULL) {
  if (file.exists(path)) {
    if (!is.null(caption)) cat(sprintf("%s\n", caption))
    knitr::include_graphics(path, dpi = 300, auto_pdf = FALSE)
  }
}


```


---


# Organoids data - global alterations enrichmnet

\



Included data of fused dorsal-ventral organoids:

- 17D17V - healthy (CTRL)
- 21D21V - healthy (CTRL)
- 71D71V - disease (HD)
- 77D77V - disease (HD)
- 21D71V - mosaic (HD/CTRL)
- 71D21V - mosaic (HD/CTRL)

---


## Healthy vs. Disease

### Differentially expressed genes (DEG)

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "HD_vs_CTRL.svg"), "Volcano plot")


```

- **Downregulated genes in disease condition**
- **Upregulated genes in disease condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="HD_vs_CTRL.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```


\

Genes for enrichment were selected based on the **Mann-Whitney U test** ($p < 0.05$). The direction of deregulation was determined using the log-fold change ($log(FC)$) values:

* **Upregulated genes:** $log(FC) > 0.25$
* **Downregulated genes:** $log(FC) < -0.25$

\ 

### Gene Interactions


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', 'HD_VS_CTRL_GI.html', 'Gene Interactions interactive network'))

```


\ 

### GO-TERM


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', 'HD_VS_CTRL_GO.html', 'GO-TERM interactive network'))

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="GO_terms_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download GO-TERM data
  </a>
</div>
')

```

\ 

### KEGG


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', 'HD_VS_CTRL_KEGG.html', 'KEGG interactive network'))

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="KEGG_terms_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download KEGG data
  </a>
</div>
')

```


\ 

### REACTOME


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', 'HD_VS_CTRL_REACTOME.html', 'REACTOME interactive network'))

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="REACTOME_terms_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download REACTOME data
  </a>
</div>
')

```


### ML-Driven Data Selection

Included top GO-TERM, KEGG, and REACTOME selected by custom ML algorithms


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', 'HD_VS_CTRL_automl.html', 'ML-Driven interactive network'))

```


\


---

## Healthy vs. 21D71V

### Differentially expressed genes (DEG)

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "21D71V_vs_CTRL.svg"), "Volcano plot")


```

- **Downregulated genes in 21D71V condition**
- **Upregulated genes in 21D71V condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D71V_vs_CTRL.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```

\

Genes for enrichment were selected based on the **Mann-Whitney U test** ($p < 0.05$). The direction of deregulation was determined using the log-fold change ($log(FC)$) values:

* **Upregulated genes:** $log(FC) > 0.25$
* **Downregulated genes:** $log(FC) < -0.25$

\ 

### Gene Interactions


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '21D71V_vs_CTRL_GI.html', 'Gene Interactions interactive network'))

```


\ 

### GO-TERM


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '21D71V_vs_CTRL_GO.html', 'GO-TERM interactive network'))

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D71V_vs_CTRL_GO_terms_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download GO-TERM data
  </a>
</div>
')

```

\ 

### KEGG


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '21D71V_vs_CTRL_KEGG.html', 'KEGG interactive network'))

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D71V_vs_CTRL_KEGG_terms_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download KEGG data
  </a>
</div>
')

```


\ 

### REACTOME


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '21D71V_vs_CTRL_REACTOME.html', 'REACTOME interactive network'))

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D71V_vs_CTRL_REACTOME_terms_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download REACTOME data
  </a>
</div>
')

```


### ML-Driven Data Selection

Included top GO-TERM, KEGG, and REACTOME selected by custom ML algorithms


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '21D71V_vs_CTRL_automl.html', 'ML-Driven interactive network'))

```

\

---

## Healthy vs. 71D21V

### Differentially expressed genes (DEG)

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "71D21V_vs_CTRL.svg"), "Volcano plot")


```

- **Downregulated genes in 71D21V condition**
- **Upregulated genes in 71D21V condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D21V_vs_CTRL.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```

\

Genes for enrichment were selected based on the **Mann-Whitney U test** ($p < 0.05$). The direction of deregulation was determined using the log-fold change ($log(FC)$) values:

* **Upregulated genes:** $log(FC) > 0.25$
* **Downregulated genes:** $log(FC) < -0.25$

\ 

### Gene Interactions


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '71D21V_vs_CTRL_GI.html', 'Gene Interactions interactive network'))

```


\ 

### GO-TERM


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '71D21V_vs_CTRL_GO.html', 'GO-TERM interactive network'))

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D21V_vs_CTRL_GO_terms_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download GO-TERM data
  </a>
</div>
')

```

\ 

### KEGG


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '71D21V_vs_CTRL_KEGG.html', 'KEGG interactive network'))

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D21V_vs_CTRL_KEGG_terms_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download KEGG data
  </a>
</div>
')

```


\ 

### REACTOME


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '71D21V_vs_CTRL_REACTOME.html', 'REACTOME interactive network'))

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D21V_vs_CTRL_REACTOME_terms_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download REACTOME data
  </a>
</div>
')

```


### ML-Driven Data Selection

Included top GO-TERM, KEGG, and REACTOME selected by custom ML algorithms


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '71D21V_vs_CTRL_automl.html', 'ML-Driven interactive network'))

```

\

---

\

# Disclaimer

The analysis was performed through the non-profit and open-source library **GEDSpy**.
Remember, *in silico* analysis must be validated *in vitro* or *in vivo*. For more information, visit [GitHub](https://github.com/jkubis96/GEDSpy) or contact us. 

---

\

