---
title: "GTF-tool - extending 5' & 3' UTR"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly       
    highlight: tango
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    self_contained: true
---


```{r setup, include=FALSE}
install_if_missing <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
  }
}

packages <- c("knitr", "dplyr", "kableExtra")
lapply(packages, install_if_missing)

library(knitr)
library(dplyr)
library(kableExtra)

set.seed(123)



```


---


# IGV visualization of reads mapped to extended UTR regions


---

\

## Top 5 genes with the highest number of additional reads mapped to the 3′ UTR

### NDUFB10

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR3/NDUFB10.png"), auto_pdf = F)

```

```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/NDUFB10.pdf', 'PDF'))

```

\


### BEST1

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR3/BEST1.png"), auto_pdf = F)

```

```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/BEST1.pdf', 'PDF'))

```


\


### NUP210L

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR3/NUP210L.png"), auto_pdf = F)

```

```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/NUP210L.pdf', 'PDF'))

```

\

### PTMA

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR3/PTMA.png"), auto_pdf = F)

```

```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/PTMA.pdf', 'PDF'))

```

\

### DIPK1A

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR3/DIPK1A.png"), auto_pdf = F)

```

```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/DIPK1A.pdf', 'PDF'))

```

\

\

---

\

## Top 5 genes with the highest number of additional reads mapped to the 5′ UTR

### ARGLU1

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR5/ARGLU1.png"), auto_pdf = T)

```

```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/ARGLU1.pdf', 'PDF'))

```


\


### TXNIP

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR5/TXNIP.png"), auto_pdf = F)

```

```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/TXNIP.pdf', 'PDF'))

```

\


### NACA

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR5/NACA.png"), auto_pdf = F)

```

```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/NACA.pdf', 'PDF'))

```

\

### RACK1

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR5/RACK1.png"), auto_pdf = F)

```

```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/RACK1.pdf', 'PDF'))

```


\

### MYL6

\

```{r echo=FALSE, out.width = '100%', fig.align="center"}

knitr::include_graphics(file.path(getwd(), "gtf/UTR5/MYL6.png"), auto_pdf = F)

```


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Display %s
  </a>
</div>
', 'gtf/UTR3/MYL6.pdf', 'PDF'))

```


\



---

\

# Disclaimer

The analysis was performed through the non-profit and open-source library **GTF-tool**.
Remember, *in silico* analysis must be validated *in vitro* or *in vivo*. For more information, visit [GitHub](https://github.com/jkubis96/GTF-tool) or contact us. 

---

\

