---
title: "JDtI - data integration and analysis"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly       
    highlight: tango
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    self_contained: true
    css: "custom.css"
---


```{r setup, include=FALSE}
install_if_missing <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
  }
}

packages <- c("knitr", "dplyr", "kableExtra")
lapply(packages, install_if_missing)

library(knitr)
library(dplyr)
library(kableExtra)

set.seed(123)



show_image <- function(path, caption = NULL, width = NULL, height = NULL) {
  if (file.exists(path)) {
    if (!is.null(caption)) cat(sprintf("%s\n", caption))
    knitr::include_graphics(path, dpi = 300, auto_pdf = FALSE)
  }
}


```


---


# Embrionic brains data integration

\



Integrated data of separate dorsal and ventral embryonic brain parts:

- BAC21D - healthy
- BAC21V - healthy
- HU128/21D - heterozygous-disease
- HU128/21V - heterozygous-disease
- YAC128D - homozygous-disease
- YAC128V - homozygous-disease

---

### Quality Control

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "gene_hist_embryos.jpeg"), "Genes per cell")

```

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "cell_hist_embryos.jpeg"), "Cells per cluster")

```

\


### Dimensionality reduction - PCA

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "pca_embryos.svg"), "PCA-plot")

```

\

### PC selection

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
  show_image(file.path(getwd(), "pca_knee_embryos.svg"), "Knee plot")
```


\

### Dimensionality reduction - UMAP - harmonized data


\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
  show_image(file.path(getwd(), "integrated_data_set_harmonized_embryos.svg"), "UMAP plot - sets")
```

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
  show_image(file.path(getwd(), "integrated_data_subtypes_harmonized_embryos.svg"), "UMAP plot - subtypes")
```


\

### Dimensionality reduction - UMAP - non-harmonized data


\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
  show_image(file.path(getwd(), "integrated_data_set_embryos.svg"), "UMAP plot - sets")
```

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
  show_image(file.path(getwd(), "integrated_data_subtypes_harmonized_embryos.svg"), "UMAP plot - subtypes")
```



\


### Subtypes similarity


\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
  show_image(file.path(getwd(), "similarity_umap_embryos.svg"), "UMAP - cor~disatance similarity")
```


---

\

# Disclaimer

The analysis was performed through the non-profit and open-source library **JDtI**.
Remember, *in silico* analysis must be validated *in vitro* or *in vivo*. For more information, visit [GitHub](https://github.com/jkubis96/JDtI) or contact us. 

---

\
