---
title: "CFI - single cell (subtypes) interactions HD alteration study"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly       
    highlight: tango
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    self_contained: true
    css: "custom.css"
---


```{r setup, include=FALSE}
install_if_missing <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
  }
}

packages <- c("knitr", "dplyr", "kableExtra")
lapply(packages, install_if_missing)

library(knitr)
library(dplyr)
library(kableExtra)

set.seed(123)



show_image <- function(path, caption = NULL, width = NULL, height = NULL) {
  if (file.exists(path)) {
    if (!is.null(caption)) cat(sprintf("%s\n", caption))
    knitr::include_graphics(path, dpi = 300, auto_pdf = FALSE)
  }
}


```


---



# Organoids data - subtypes functionality enrichment

\



Included data of fused dorsal-ventral organoids:

- 17D17V - healthy (CTRL)
- 21D21V - healthy (CTRL)
- 71D71V - disease (HD)
- 77D77V - disease (HD)
- 21D71V - mosaic (HD/CTRL)
- 71D21V - mosaic (HD/CTRL)

---


## Healthy vs. Disease

### Differentially expressed ligand-receptor genes

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "HDvsCTRL_connctions.svg"), "Volcano plot")


```

- **Downregulated genes in disease condition**
- **Upregulated genes in disease condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="HDvsCTRL_connctions.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```

\

---

## Healthy vs. 21D71V

### Differentially expressed ligand-receptor genes

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "HDvsMOSAIC21D71V_connctions.svg"), "Volcano plot")


```

- **Downregulated genes in 21D71V condition**
- **Upregulated genes in 21D71V condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="HDvsMOSAIC21D71V_connctions.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```



\

---

## Healthy vs. 71D21V

### Differentially expressed ligand-receptor genes

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "HDvsMOSAIC71D21V_connctions.svg"), "Volcano plot")


```

- **Downregulated genes in 71D21V condition**
- **Upregulated genes in 71D21V condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="HDvsMOSAIC71D21V_connctions.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```

\

---

## Deregulated ligand and receptor genes across organoid types

\

Ligand and receptor genes were selected based on the **Mann-Whitney U test** ($p < 0.05$). The direction of deregulation was determined using the log-fold change ($log(FC)$) values:

* **Upregulated genes:** $log(FC) > 0$
* **Downregulated genes:** $log(FC) < 0$

Selected genes were further annotated using information retrieved from **GeneCards**. To enhance the functional analysis, the data were curated using **Large Language Models (LLMs)**, specifically focusing on roles in **developmental processes** and **regulatory functionalities**.

\

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

df <- read.csv('db/organoids.csv', check.names = FALSE)

DT::datatable(df)

```

\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="db/organoids.csv" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data with enrichment
  </a>
</div>
')

```


\


---


# Embryos data - subtypes functionality enrichment

\



Included data of separated dorsal and ventral embryonic brain parts:

- BAC21D - healthy (CTRL)
- BAC21V - healthy (CTRL)
- HU128/21D - heterozygous disease (HD/CTRL)
- HU128/21V - heterozygous disease (HD/CTRL)
- YAC128D - homozygous disease (HD)
- YAC128V - homozygous disease (HD)

---


## Healthy (D) vs. Disease (YAC128D)

### Differentially expressed ligand-receptor genes

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "disease_yac_dorsal_vs_healthy_dorsal_connctions.svg"), "Volcano plot")


```

- **Downregulated genes in YAC128D condition**
- **Upregulated genes in YAC128D condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="disease_yac_dorsal_vs_healthy_dorsal_connctions.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```

\

---

## Healthy (V) vs. Disease (YAC128V)

### Differentially expressed ligand-receptor genes

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "disease_yac_ventral_vs_healthy_ventral_connctions.svg"), "Volcano plot")


```

- **Downregulated genes in YAC128V condition**
- **Upregulated genes in YAC128V condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="disease_yac_ventral_vs_healthy_ventral_connctions.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```



\

---

## Healthy (D) vs. Disease (HU128/21D)

### Differentially expressed ligand-receptor genes

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "disease_hu_dorsal_vs_healthy_dorsal_connctions"), "Volcano plot")


```

- **Downregulated genes in HU128/21D condition**
- **Upregulated genes in HU128/21D condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="disease_hu_dorsal_vs_healthy_dorsal_connctions.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```

\

---

## Healthy (V) vs. Disease (HU128/21V)

### Differentially expressed ligand-receptor genes

\

```{r echo=FALSE, out.width = '100%', fig.align="center", results='asis'}
show_image(file.path(getwd(), "disease_hu_ventral_vs_healthy_ventral_connctions.svg"), "Volcano plot")


```

- **Downregulated genes in HU128/21V condition**
- **Upregulated genes in HU128/21V condition**



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="disease_hu_ventral_vs_healthy_ventral_connctions.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data
  </a>
</div>
')

```

\

--- 

## Deregulated ligand and receptor genes across embryonic brain parts and types

\

Ligand and receptor genes were selected based on the **Mann-Whitney U test** ($p < 0.05$). The direction of deregulation was determined using the log-fold change ($log(FC)$) values:

* **Upregulated genes:** $log(FC) > 0$
* **Downregulated genes:** $log(FC) < 0$

Selected genes were further annotated using information retrieved from **GeneCards**. To enhance the functional analysis, the data were curated using **Large Language Models (LLMs)**, specifically focusing on roles in **developmental processes** and **regulatory functionalities**.

\

```{r echo=FALSE, message=FALSE, warning=FALSE, results='asis'}

df <- read.csv('db/embryos.csv', check.names = FALSE)
df$`Functional Description` <- iconv(df$`Functional Description`, from = "UTF-8", to = "UTF-8", sub = "")
DT::datatable(df)

```

\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="db/embryos.csv" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download DEG data with enrichment
  </a>
</div>
')

```


---

\

# Disclaimer

The analysis was performed through the non-profit and open-source library **CFI**.
Remember, *in silico* analysis must be validated *in vitro* or *in vivo*. For more information, visit [GitHub](https://github.com/jkubis96/CFI) or contact us. 

---

\

