---
title: "CFI - single cell (subtypes) functionality enrichment"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly       
    highlight: tango
    toc: true
    toc_float: true
    number_sections: true
    df_print: paged
    self_contained: true
    css: "custom.css"
---


```{r setup, include=FALSE}
install_if_missing <- function(pkg) {
  if (!require(pkg, character.only = TRUE)) {
    install.packages(pkg, dependencies = TRUE)
  }
}

packages <- c("knitr", "dplyr", "kableExtra")
lapply(packages, install_if_missing)

library(knitr)
library(dplyr)
library(kableExtra)

set.seed(123)



show_image <- function(path, caption = NULL, width = NULL, height = NULL) {
  if (file.exists(path)) {
    if (!is.null(caption)) cat(sprintf("%s\n", caption))
    knitr::include_graphics(path, dpi = 300, auto_pdf = FALSE)
  }
}


```


---


# Organoids data - subtypes functionality enrichment

\



Included data of fused dorsal-ventral organoids:

- 17D17V - healthy (CTRL)
- 21D21V - healthy (CTRL)
- 71D71V - disease (HD)
- 77D77V - disease (HD)
- 21D71V - mosaic (HD/CTRL)
- 71D21V - mosaic (HD/CTRL)

---


## Organoid 17D17V

### Cell-Cell interactions



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="17D17V/17q_dorsal_17q_ventral_cell_con.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download cell-cell interactions data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '17D17V/17q_dorsal_17q_ventral_cell_con.html', 'Cell-Cell interaction interactive network'))

```

 

### Cell subtypes gene markers enrichment (cell functionality)



```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="17D17V/17q_dorsal_17q_ventral_GO_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download GO-TERM data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="17D17V/17q_dorsal_17q_ventral_KEGG_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download KEGG data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="17D17V/17q_dorsal_17q_ventral_REACTOME_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download REACTOME data
  </a>
</div>
')

```

\

---


## Organoid 21D21V

### Cell-Cell interactions



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D21V/21q_dorsal_21q_ventral_cell_con.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download cell-cell interactions data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '21D21V/21q_dorsal_21q_ventral_cell_con.html', 'Cell-Cell interaction interactive network'))

```

 

### Cell subtypes gene markers enrichment (cell functionality)



```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D21V/21q_dorsal_21q_ventral_GO_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download GO-TERM data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D21V/21q_dorsal_21q_ventral_KEGG_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download KEGG data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D21V/21q_dorsal_21q_ventral_REACTOME_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download REACTOME data
  </a>
</div>
')

```


\

---


## Organoid 71D71V

### Cell-Cell interactions



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D71V/71q_dorsal_71q_ventral_cell_con.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download cell-cell interactions data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '71D71V/71q_dorsal_71q_ventral_cell_con.html', 'Cell-Cell interaction interactive network'))

```

 

### Cell subtypes gene markers enrichment (cell functionality)



```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D71V/71q_dorsal_71q_ventral_GO_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download GO-TERM data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D71V/71q_dorsal_71q_ventral_KEGG_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download KEGG data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D71V/71q_dorsal_71q_ventral_REACTOME_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download REACTOME data
  </a>
</div>
')

```


\

---


## Organoid 77D77V

### Cell-Cell interactions



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="77D77V/77q_dorsal_77q_ventral_cell_con.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download cell-cell interactions data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '77D77V/77q_dorsal_77q_ventral_cell_con.html', 'Cell-Cell interaction interactive network'))

```

 

### Cell subtypes gene markers enrichment (cell functionality)



```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="77D77V/77q_dorsal_77q_ventral_GO_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download GO-TERM data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="77D77V/77q_dorsal_77q_ventral_KEGG_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download KEGG data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="77D77V/77q_dorsal_77q_ventral_REACTOME_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download REACTOME data
  </a>
</div>
')

```



\

---


## Organoid 21D71V

### Cell-Cell interactions



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D71V/21q_dorsal_71q_ventral_cell_con.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download cell-cell interactions data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '21D71V/21q_dorsal_71q_ventral_cell_con.html', 'Cell-Cell interaction interactive network'))

```

 

### Cell subtypes gene markers enrichment (cell functionality)



```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D71V/21q_dorsal_71q_ventral_GO_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download GO-TERM data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D71V/21q_dorsal_71q_ventral_KEGG_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download KEGG data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="21D71V/21q_dorsal_71q_ventral_REACTOME_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download REACTOME data
  </a>
</div>
')

```



\

---


## Organoid 71D21V

### Cell-Cell interactions



\

```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D21V/71q_dorsal_21q_ventral_cell_con.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download cell-cell interactions data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}

cat(sprintf('
<div style="text-align:center; margin:10px 0;">
  <a href="%s" target="_blank"
     style="
       display:inline-block;
       padding:12px 20px;
       font-size:15px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#6A11CB,#2575FC);
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:0.2s ease;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'"
     onmouseout="this.style.transform=\'scale(1)\'"
  >
    Open %s
  </a>
</div>
', '71D21V/71q_dorsal_21q_ventral_cell_con.html', 'Cell-Cell interaction interactive network'))

```

 

### Cell subtypes gene markers enrichment (cell functionality)



```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D21V/71q_dorsal_21q_ventral_GO_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download GO-TERM data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D21V/71q_dorsal_21q_ventral_KEGG_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download KEGG data
  </a>
</div>
')

```


```{r echo=FALSE, results='asis'}
cat('
<div style="text-align:center; margin:20px 0;">
  <a href="71D21V/71q_dorsal_21q_ventral_REACTOME_r.xlsx" download 
     style="
       display:inline-block;
       padding:12px 22px;
       font-size:16px;
       font-weight:600;
       color:#fff;
       background:linear-gradient(135deg,#4CAF50,#2E7D32);
       border:none;
       border-radius:8px;
       text-decoration:none;
       box-shadow:0 4px 10px rgba(0,0,0,0.15);
       transition:all 0.2s ease-in-out;
     "
     onmouseover="this.style.transform=\'scale(1.05)\'; this.style.boxShadow=\'0 6px 14px rgba(0,0,0,0.25)\'"
     onmouseout="this.style.transform=\'scale(1)\'; this.style.boxShadow=\'0 4px 10px rgba(0,0,0,0.15)\'"
  >
    ⬇️ Download REACTOME data
  </a>
</div>
')

```



\

---

\

# Disclaimer

The analysis was performed through the non-profit and open-source library **CFI**.
Remember, *in silico* analysis must be validated *in vitro* or *in vivo*. For more information, visit [GitHub](https://github.com/jkubis96/CFI) or contact us. 

---

\

